### 2024-04-04 project1/nsSurvey.tex
new

Nested simulation procedures, also known as stochastic on stochastic simulation, are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
The term \textit{nested} is referred to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
In a typical nested simulation procedure, an outer level simulation model generates underlying risk factors, which is referred to as the \textit{outer scenarios}.
For each outer scenario, an inner level simulation model generates scenario-wise samples of the portfolio losses, which is referred to as the \textit{inner replications}.

@@

The standard nested simulation procedure is computationally expensive with a somewhat wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario. 
Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using the inner replications from other outer scenarios. 
This is referred to as pooling. 
Different methods pool in different ways, either by a trained proxy model or by pre-defined likelihood ratio weights.
~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression proxy model to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} propose to use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the risk measure of interest.

This paper presents a survey study of some popular nested simulation procedures. 
Many procedures are proposed in the literature, but they are not directly comparable due to different error metrics, different assumptions, and different numerical examples.
Within a common analytical framework, we first summarize and compare their asymptotic rate of convergence.
Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
Furthermore, our study finds that different studies have used different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
A fair comparison among popular methods is therefore urgently needed in the literature. 
Our numerical experiment is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
Extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures.

The rest of the paper is organized as follows.
% Section~\ref{sec:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
% Section~\ref{sec:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
% Section~\ref{sec:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
% Section~\ref{sec:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
% Section~\ref{sec:computational-complexity} discusses the computational complexity of different nested simulation procedures.
% Section~\ref{sec:conclusion} concludes the paper.

\section{Problem Formulation} \label{sec:problem-formulation}

@@

@@

In supervised learning, $g(\cdot)$ can be approximated by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family $\mathcal{G}$ and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
Using the $M$ \textit{training} samples, a supervised learning-based nested simulation procedure estimates  $\rho$ by

@@

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}.$$
    \item   CVaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil} + \frac{1}{(1-\alpha) M} \sum_{i=1}^M \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}, 0 \}, $$
            where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M \rceil}$ is the $\lceil \alpha M \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_M)$. 
            Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.
\end{enumerate}

@@

Instead of using a supervised learning model,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
This method is also referred to as importance sampling.
Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
Specifically,
$$ Y = Y(H, X), $$
where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
$$ Y_{ij} = Y(H_{ij}, X_i), $$
where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
Suppose that one can generate random variable H from some sampling
distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{LR}}_N(X_i)), $$ where the inner replications are pooled by the likelihood ratio weights with
$$\hat{g}^{\text{LR}}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$

The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
A MLMC approach is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
Instead of pooling from the inner samples, a MLMC-based nested simulation procedure estimates $\rho$ with a multi-level Monte Carlo estimator:

\subsection{Problem Statement}

For all nested simulation procedures we are interested in the order of convergence of estimators in terms of the total simulation budget $\Gamma$.
The convergence rate of an estimator is measured by the MSE of the estimator $\hat{\rho}_{M, N}$ about the true value $\rho$.

\begin{align}
    & \text{MSE}(\hat{\rho}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
    & \text{subject to} ~~~ M \cdot N = \Gamma, 
\end{align}

where $\Gamma = M \cdot N$ is the total simulation budget\footnote{For a MLMC-based nested simulation procedure, the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.}. 
For a given nested simulation procedure, we are interested in the optimal budget allocation that minimizes the MSE of the estimator $\hat{\rho}_{M, N}$.

>>>>

Nested simulation procedures are commonly used in financial engineering to estimate risk measures for portfolios of complex financial derivatives. 
The term \textit{nested} is referred to a nested estimation problem, in which the estimation of the risk measure requires two levels of Monte Carlo (MC) simulations.
In a typical nested simulation procedure, an outer level simulation model generates underlying risk factors, which is referred to as the \textit{outer scenarios}.
For each outer scenario, an inner level simulation model generates scenario-wise samples of the portfolio losses, which is referred to as the \textit{inner replications}.

@@

The standard nested simulation procedure is computationally expensive with a somewhat wasteful use of the simulation budget, as only the inner replications from the same outer scenario are used in estimating the scenario-wise portfolio loss for that outer scenario. 
Subsequent research efforts have been made to improve the efficiency of nested simulation procedures by using the inner replications from other outer scenarios. 
This is referred to as pooling. 
Different methods pool in different ways, either by a trained proxy model or by pre-defined likelihood ratio weights.
~\cite{broadie2015risk} propose a regression-based nested simulation procedure, which uses a trained regression proxy model to estimate the scenario-wise portfolio loss for an outer scenario by pooling the inner replications from all outer scenarios.
For risk measures in certain forms,~\cite{broadie2015risk} show that it is optimal to allocate all simulation budget to the outer level simulation, and the inner replication should be kept to a minimum of $1$.
Similarly,~\cite{hong2017kernel},~\cite{feng2020optimal}, and~\cite{zhang2022sample} use a kernel smoothing model, a likelihood ratio model, and a kernel ridge regression model as proxies to pool the inner replications from all outer scenarios.
In simulation studies, this approach of using a model of a simulation model is known as metamodeling, and the models of a simulation model are also referred to as metamodels~\citep{barton1998simulation}.
Another line of research is the multi-level Monte Carlo (MLMC) method analyzed in~\cite{giles2019multilevel}, which is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest.

This paper presents a survey study of some popular nested simulation procedures. 
Many procedures are proposed in the literature, but they are not directly comparable due to different error metrics, different assumptions, and different numerical examples.
Within a common analytical framework, we first summarize and compare their asymptotic rate of convergence.
Their asymptotic convergence results are closely examined for their assumptions that guarantee the convergence.
Furthermore, our study finds that different studies propose different examples in their numerical experiments, which introduces unfair advantages for certain simulation procedures over others. 
A fair comparison among popular methods is therefore urgently needed in the literature. 
Our numerical experiment is the first of its kind to subject back all the aforementioned simulation procedures to a complete and unbiased comparison. 
Extensive numerical experiments are conducted to show, in practical examples, how well the finite-sample performance of a method matches its theoretical convergence behavior. 
With our numerical examples, we compare the nested simulation procedures for different payoff complexity, problem dimensions, and risk measures.

The rest of the paper is organized as follows.
Section~\ref{sec1:problem-formulation} introduces the nested simulation procedure and the standard Monte Carlo estimator.
Section~\ref{sec1:asymptotic-convergence} provides new theoretical results on the convergence of existing nested simulation procedures.
Section~\ref{sec1:convergence-orders} summarizes the asymptotic convergence orders and the critical assumptions of nested simulation procedures in the literature.
Section~\ref{sec1:numerical-experiments} presents the numerical experiments and the comparisons of different nested simulation procedures with respect to different risk measures, problem dimensions, and payoff complexities.
Section~\ref{sec1:computational-complexity} discusses the computational complexity of different nested simulation procedures.
Section~\ref{sec1:conclusion} concludes the paper.

\section{Problem Formulation} \label{sec1:problem-formulation}

@@

The multi-level Monte Carlo (MLMC) method is a variance reduction technique that uses a hierarchy of approximations to the quantity of interest, and it uses the difference between the approximations to reduce the variance of the estimator.
The MLMC method is particularly useful when the quantity of interest is expensive to evaluate, and the standard Monte Carlo estimator has a high variance.
The MLMC method estimates $\rho$ with a multi-level Monte Carlo estimator:

@@

In supervised learning, $g(\cdot)$ can be approximated by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$, which is based on a chosen function family $\mathcal{G}$ and observations from the standard nested simulation procedure.
Consider the observation pairs $(X_i, \hat{g}_N(X_i))$ for $i \in \{1, \dots, M\}$ as training data, we can use supervised learning to approximate $g(\cdot)$ by $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ and to pool the inner replications from all outer scenarios.
Using the $M$ \textit{training} samples, a nested Monte Carlo estimator of $\rho$ is given by

@@

\begin{enumerate}
    \item   Nested expectation form:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = \frac{1}{M'} \sum_{i=1}^{M'} h(\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i)); ~~~ \tilde{X}_i \sim F_X.$$
    \item   VaR:
            $$\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}.$$
    \item   CVaR:
            \begin{align*}
                \hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'} & = (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}  \\
                & + \frac{1}{(1-\alpha) M'} \sum_{i=1}^{M'} \max \{\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_i) - (\hat{g}^{\text{SL}}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}, 0 \}, 
            \end{align*}
\end{enumerate}
where $(\hat{g}_{M, N}(\tilde{\mathbf{X}}))_{\lceil \alpha M' \rceil}$ is the $\lceil \alpha M' \rceil$-th order statistic of $\hat{g}^{\text{SL}}_{M, N}(\tilde{X}_1), \dots, \hat{g}_{M, N}(\tilde{X}_{M'})$. 
Note that $\hat{g}^{\text{SL}}_{M, N}(\cdot)$ is derived from the training samples $(X_1, \hat{g}_N(X_1)), \dots, (X_M, \hat{g}_N(X_M))$.

We are interested in minimizing the MSE of the supervised learning-based nested simulation estimator with supervised learning $\hat{\rho}^{\text{SL}, \text{Train}}_{M, N}$ and $\hat{\rho}^{\text{SL}, \text{Test}}_{M, N, M'}$ subject to the total simulation budget $\Gamma$.

\begin{align}
    & \min_{M, N}  & \text{MSE}(\hat{\rho}^{\text{SL}}_{M, N}) = \mathbb{E} \left[ \left( \hat{\rho}^{\text{SL}}_{M, N} - \rho \right)^2 \right] \nonumber \\
    & \text{subject to} & M \cdot N = \Gamma 
\end{align}

@@

Instead of using a supervised learning model as proxy,~\cite{zhang2022sample} uses the likelihood ratio weights to pool the inner replications from all outer scenarios.
Here, we restrict our attention to problems in the nested expectation form whose outer scenarios characterize the stochasticity of the inner simulation model. 
Specifically,
$$ Y = Y(H, X), $$
where $H$ is a random variable whose distribution is specified by the outer scenarios $X$. 
We denote the conditional distribution of $H|X$ by $f_{H|X}$. 
For a specific scenario $X_i$, we write $f_{H|X}(\cdot |X_i)$. 
To reconcile with previously established notations, we note that inner simulation outputs $Y_{ij}$ can be written as
$$ Y_{ij} = Y(H_{ij}, X_i), $$
where $H_{ij} \sim f_{H|X}(\cdot |X_i)$.
Suppose that one can generate random variable H from some sampling
distribution $f_H$. Then, the likelihood ratio estimator of $\rho$ is given by
$$\hat{\rho}^{\text{LR}}_{M,N} = \frac{1}{M} \sum_{i=1}^M h(\hat{g}^{\text{LR}}_N(X_i)), $$ where the inner replications are pooled by the likelihood ratio weights with
$$\hat{g}^{\text{LR}}_N(X_i) = \frac{1}{N} \sum_{j=1}^N Y(H_j, X_i) \frac{f_{H|X}(H_{j}|X_i)}{f_H(H_{ij})}, \;\;\; H_j \sim f_H, \;\;\; i=1, \dots, M.$$

With a total simulation budget $\Gamma$, we are interested in the order of convergence of estimators for all nested simulation procedures, which is measured by their MSE about the risk measure $\rho$.

\begin{align}
    & \min ~~~ \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
    & \text{subject to} ~~~ M \cdot N = \Gamma, 
\end{align}

where $\Gamma$ is the total simulation budget for all nested simulation procedures considered in this study.
A special case is the MLMC method, where the total simulation budget $\Gamma$ is the sum of the computational budget at all levels.

\section{Asymptotic Analysis} \label{sec1:asymptotic-convergence}
In this section, we summarize the existing asymptotic convergence results of the nested simulation procedures in the literature, and we compare their critical assumptions that guarantee the convergence.

\begin{table}[ht]
    \centering
    \footnotesize
    \begin{tabular}{|l|c|c|c|c|c|}
    \hline
    \textbf{Estimator for} $g(X)$ & \textbf{Smooth} $h$ & \textbf{Lipschitz}(\textbf{hockey-stick} $h$) & \textbf{Indicator} $h$ & \textbf{VaR} & \textbf{CVaR} \\
    \hline
    Standard Monte Carlo & $\star$ & $\star$($\checkmark$) & $\checkmark$ & $\checkmark$ & $\times$ \\
    \hline
    Multi-level Monte Carlo & $\times$ & $\times$($\times$) & $\checkmark$ & $\times$ & $\times$ \\
    \hline
    Regression & $\checkmark$ & $\checkmark$($\checkmark$) & $\times$ & $\times$ & $\times$ \\
    \hline
    Kernel smoothing & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
    \hline
    Kernel ridge regression & $\Diamond$ & $\times$($\Diamond$) & $\Diamond$ & $\Diamond$ & $\Diamond$ \\
    \hline
    Likelihood ratio & $\checkmark$ & $\times$($\checkmark$) & $\checkmark$ & $\times$ & $\times$ \\
    \hline
    \end{tabular}
    \caption{Existing asymptotic convergence results of nested simulation procedures for MSE}
    \label{tab1:asymConv-mse}
\end{table}

Table~\ref{tab1:asymConv-mse} summarizes the existing asymptotic convergence results of nested simulation procedures for MSE in the literature.
A $\checkmark$ indicates there exists an asymptotic convergence result for the corresponding estimator,
a $\times$ indicates there does not exist an asymptotic convergence result, 
a $\star$ indicates an asymptotic result is not available in the literature but is provided in this study, and
a $\Diamond$ indicates the asymptotic convergence result exists in the literature but in a weaker form.
~\cite{gordy2010nested} provide the asymptotic convergence results for the standard nested simulation procedure with hockey-stick $h$, indicator $h$ and VaR.
Their CVaR analysis is incomplete as the VaR is assumed to be known but not estimated in the convergence proof.
When the VaR is known, the CVaR analysis reduces to the nested expectation form with $h$ being a hockey-stick function.
~\cite{giles2019multilevel} provide the asymptotic convergence results for the MLMC method with an indicator $h$.
~\cite{broadie2015risk} provide the asymptotic convergence results for the regression-based nested simulation procedure with smooth $h$ and Lipschitz continuous $h$.
The Lipschitz continuous family includes the hockey-stick function as a special case, thus the convergence result for the hockey-stick function is implied.
~\cite{hong2017kernel} and~\cite{zhang2022sample} provide the asymptotic convergence results with the nested expectation form for the kernel smoothing-based procedure and likelihood ratio-based nested simulation procedure, respectively.
The convergence results for a Lipschitz continuous $h$ cannot be directly inferred from the analysis for a hockey-stick function.

While most of the literature focuses on the MSE of the estimator of $\rho$,~\cite{wang2022smooth} analyze the asymptotic convergence of the estimator of $\rho$ in terms of the absolute error.
Let $\hat{\rho}$ be the estimator of $\rho$. Its absolute error about $\rho$ is defined as

$$
\mbox{Absolute Error}\left(\hat{\rho}\right) = \left| \hat{\rho} - \rho \right|.
$$

In~\cite{wang2022smooth}, the authors of the KRR-based nested simulation procedures claim to have bridged the gap between the cubic and square root convergence rates of nested simulation procedures. However, they analyze convergence in probabilistic order, and it is only applicable in terms of the absolute error. 
Instead of showing the convergence of the KRR-based estimator in terms of MSE as in~\cite{gordy2010nested}, we show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error.
Our findings in Section~\ref{sec1:connection-mse-absolute-error} show that the analysis of ~\cite{wang2022smooth} indeed bridges the gap, but only in terms of the absolute error.

\subsection{Connections between Convergence in MSE and Absolute Error} \label{sec1:connection-mse-absolute-error}

This section establishes the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation procedures.
In order to show the connections between the convergence in MSE and the convergence in probabilistic order for absolute error, we first need to state the definition for a sequence of random variables to converge in those two forms.

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$, that is, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$ if 
    $$
        \exists C \limsup_{M} \frac{\mathbb{E} \left[\left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C
    $$
\end{definition}

\begin{definition}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    We write $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$, that is $\hat{\rho}_{\Gamma}$ converges in probabilistic order $k$ to $\rho$ if for large enough $\Gamma$,
    $$
        \forall \epsilon > 0 \exists C \mathbb{P} \left( \left| \hat{\rho}_{\Gamma} - \rho \right| \geq C \Gamma^{-k} \right) \leq \epsilon 
    $$
\end{definition}

We start by showing the convergence in probabilistic order from the convergence in MSE.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathcal{O} \left( \Gamma^{-k} \right)$.
Then, from the definition of convergence in MSE, there exists a constant $C$ such that 
$$
    \limsup_{M} \frac{\mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right]}{\Gamma^{-k}} \leq C.
$$
Hence, there exists some $\Gamma$ such that for all $\gamma \geq \Gamma$,
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \right] \leq C\gamma^{-k}.
$$
The convergence in probabilistic order can be shown by separating the expectation into two parts: tail and non-tail.
$$
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| \leq d\gamma^s\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] \leq C\gamma^{-k}.
$$
The first term is always positive, and the second term can be bounded from below by the indicator function.
\begin{align*}
\mathbb{E} \left[ \left(\hat{\rho}_{\gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\}} \right] 
& \geq \mathbb{E} \left[ d^2 \gamma^{2s} \cdot \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s\} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \} \right] \\
& = d^2 \gamma^{2s} \cdot \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right)
\end{align*}

Combining bounds on the two terms, we have

$$
    d^2 \gamma^{2s} \mathbb{P} \left(|\hat{\rho}_{\gamma} - \rho| > d\gamma^s \right) \leq C \gamma^{-k}.
$$

Let $s = -\frac{k}{2}$. Arranging the terms, we have

$$
    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > d\gamma^{-\frac{k}{2}} \right) \leq \frac{C}{d^2}
$$

Hence, for all $\epsilon >0$, there exist $C^* = \sqrt{\frac{C}{\epsilon}}$ such that for all $\gamma \geq \Gamma$,

$$
    \mathbb{P} \left( |\hat{\rho}_{\gamma} - \rho| > C^*\gamma^{-\frac{k}{2}} \right) \leq \epsilon
$$

In essence, the above is the definition of convergence in probabilistic order, that is,

$$
    \left| \hat{\rho}_{\gamma} - \rho \right| = \mathcal{O}_\mathbb{P} \left( \Gamma^{-\frac{k}{2}} \right)
$$

\begin{theorem} \label{thm1:convergence-mse-prob}
    Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$. 
    If $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $k$, then $\hat{\rho}_{\Gamma}$ converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.
\end{theorem}

To the best of our knowledge, Theorem~\ref{thm1:convergence-mse-prob} has not been explicitly stated in the literature.
It is the first result that shows the connections between the convergence in MSE and the convergence in probabilistic order for absolute error in the context of nested simulation.
Theorem~\ref{thm1:convergence-mse-prob} is a general result that can be applied to any nested simulation procedure that converges in MSE to $\rho$ in order $k$.
If the estimator converges in MSE to $\rho$ in order $k$, then it converges in probabilistic order to $\rho$ in order $\frac{k}{2}$.

While the convergence in MSE implies the convergence in probabilistic order, the converse is not necessarily true.
Similarly, the above argument is applied in reverse.
Let $\hat{\rho}_{\Gamma}$ be an estimator of $\rho$ with a simulation budget of $\Gamma$, and assume that $|\hat{\rho}_{\Gamma} - \rho| = \mathcal{O}_{\mathbb{P}}(\Gamma^{-k})$.
The MSE of $\hat{\rho}_{\Gamma}$ can be separated into the same two parts.

$$
    \mathbb{E}\left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \right] = \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| \leq d\Gamma^{-2k}\}} \right] + \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right], 
$$
where the first term can be bounded from above.

\begin{align*}
    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s\}} \right] 
    & \leq d^2 \Gamma^{-2k} \cdot \mathbb{E} \left[ \mathbb{I}\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \} \right] \\
    & = d^2 \Gamma^{-2k} \cdot \mathbb{P} \left(|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^s \right) \leq d^2 \Gamma^{-2k} 
\end{align*}
However, the second term is not always bounded. 
If the random variable $\hat{\rho}_{\Gamma}$ admits a density function $f$, then the second term can be further decomposed.

\begin{align*}
    \mathbb{E} \left[ \left(\hat{\rho}_{\Gamma} - \rho\right)^2 \cdot \mathbb{I}_{\{|\hat{\rho}_{\Gamma} - \rho| > d\Gamma^{-2k}\}} \right] 
    & = \int_{-\infty}^{-d\Gamma^{-2k}} (x - \rho)^2 f(x) dx + \int_{d\Gamma^{-2k}}^{\infty} (x - \rho)^2 f(x) dx 
\end{align*}
Hence, $\hat{\rho}_{\Gamma}$ converges in MSE to $\rho$ in order $2k$ if and only if both integrals converge in order higher than $2k$. 
The above argument shows that the convergence in probabilistic order does not necessarily imply the convergence in MSE.
The convergence in probabilistic order is a weaker form of convergence than the convergence in MSE.

\subsection{Asymptotic Analysis for the Standard Nested Simulation Procedure}
In~\cite{gordy2010nested}, the authors analyze the asymptotic convergence of the standard nested simulation procedure in terms of MSE. 
The analysis is complete for the nested expectation form where $h$ is either an indicator function or a hockey-stick function and VaR. 
For the nested expectation form where $h$ is a smooth function or a Lipschitz continuous function, the analysis is incomplete.
In this section, we fill in the holes in the analysis of~\cite{gordy2010nested}.

\begin{assumption} \label{as1:sns}
    $h(g(X))$ has finite second moment, i.e., $\mathbb{E} \left[ \left( h(g(X)) \right)^2 \right] < \infty$.
\end{assumption}

\begin{assumption} \label{as1:sns-noise}
    $\hat{g}_N(X) = g(X) + \bar{Z}_N(X)$, where the simulation noise $\bar{Z}_N(X)$ has zero mean and variance $\nu(X) / N$, where the conditional variance $\nu(X)$ is bounded, i.e., there exists $C_{\nu, 1} > 0$ such that $\nu(x) \leq C_{\nu, 1}$ for all $x \in \mathbb{R}$. 
\end{assumption}

Let $\rho_M = \frac{1}{M} \sum_{i=1}^M h(g(X_i))$ be the nested Monte Carlo estimator with the true function $g$.
The MSE of the standard procedure can be decomposed into two terms.

\begin{align} \label{eq1:mse-sns}
    & \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho \right)^2 \right] \nonumber \\
    & \leq 2 \mathbb{E} \left[ \left( \hat{\rho}_{M, N} - \rho_M \right)^2 \right] 
            + 2  \mathbb{E} \left[ \left(\rho_M - \rho \right)^2 \right]  \nonumber \\
    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  \frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
    & ~~~~ + 2  \mathbb{E} \left[ \left(\frac{1}{M} \sum_{i=1}^M h\left(g(X_i) \right) - \mathbb{E}\left[ h(g(X))\right] \right)^2 \right]  \nonumber \\
    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \frac{2}{M} \text{Var}(h(g(X))) \nonumber \\
    & = 2 \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] + \mathcal{O}(M^{-1}),
\end{align}
where the last equality follows from Assumption~\ref{as1:sns}.
The analysis of the first term is different for smooth and Lipschitz continuous $h$. 
We will analyze them separately.

\subsubsection*{A Smooth Function $h$}
\begin{assumption} \label{as1:sns-smooth}
    The function $h$ has bounded first and second order derivative, i.e., there exists $C_1 > 0$ such that $|h'(x)| \leq C_1$ for all $x \in \mathbb{R}$, and there exists $C_2 > 0$ such that $|h''(x)| \leq C_2$ for all $x \in \mathbb{R}$.
\end{assumption}
Assumption~\ref{as1:sns-smooth} is similar to the smoothness assumption in~\cite{wang2022smooth}.
Since $h$ is a smooth function, Taylor expansion can be applied to the first term in Equation~\ref{eq1:mse-sns}.

\begin{align} \label{eq1:taylor-sns}
    & \mathbb{E} \left[  \left( \frac{1}{M} \sum_{i=1}^M h\left( \hat{g}_{N}(X_i) \right) -  h\left(g(X_i) \right)  \right)^2\right] \nonumber \\
    & = \mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right) +  \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right] \nonumber \\
    & \leq 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{M} \sum_{i=1}^M h'\left( g(X_i) \right) \left( \hat{g}_{ N}(X_i) - g(X_i) \right) \right)^2\right]}_{S_1} \nonumber \\
    & ~~~~ + 2 \underbrace{\mathbb{E} \left[ \left( \frac{1}{2M} \sum_{i=1}^M h''\left( z_i \right) \left( \hat{g}_{N}(X_i) - g(X_i) \right)^2 \right)^2\right]}_{S_2}
\end{align}
where the last inequality is due to $2ab \leq a^2 + b^2$ for any $a, b \in \mathbb{R}$. 
For different methods of nested estimation, each of the two terms on the right-hand side of Equation~\ref{eq1:taylor-sns} can be analyzed separately.
We start with the first term $S_1$.
